# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the activity
```{r}
library(plyr)
library(data.table)
activity <- fread("./activity.csv")
summary(activity)
activity.steps <- ddply(activity,.(date),summarize,totalSteps=sum(steps,na.rm=TRUE))    
hist(activity.steps$totalSteps)
```

## What is mean total number of steps taken per day?
```{r}
mean(activity.steps$totalSteps,na.rm=TRUE)
median(activity.steps$totalSteps,na.rm=TRUE)
```

## What is the average daily activity pattern?
```{r}
activity.aveStepsIn5Mins <- ddply(activity,.(interval),summarize,aveSteps=mean(steps,na.rm=TRUE))
ts.plot(activity.aveStepsIn5Mins$aveSteps,gpars=list(xlab="intervals",ylab="average steps"))
ts.plot(activity.aveStepsIn5Mins$aveSteps,gpars=list(xlab="intervals",ylab="average steps"))
activity.aveStepsIn5Mins[max(activity.aveStepsIn5Mins$aveSteps),]
```
## Imputing missing values
```{r}
sum(is.na(activity$step))
activity2 <- copy(activity)
activity2$temp <- ifelse(is.na(activity2$steps),0,activity2$steps)
activity2[,newSteps:=mean(temp),by=date]
activity.steps2 <- ddply(activity2,.(date),summarize,totalSteps=sum(newSteps,na.rm=TRUE))    
hist(activity.steps2$totalSteps)
mean(activity.steps2$totalSteps,na.rm=TRUE)
median(activity.steps2$totalSteps,na.rm=TRUE)
```



## Are there differences in activity patterns between weekdays and weekends?
```{r}
Sys.setlocale("LC_TIME", "C")
activity2$date <- as.Date(activity2$date)
activity2[,weekday:=weekdays(date)]
activity2[,day:=ifelse(weekday %in% c("Saturday","Sunday"),"weekend","weekday")]
activity2.aveStepsIn5Mins <- ddply(activity2,.(interval,day),summarize,aveSteps=mean(steps,na.rm=TRUE))
library(lattice)
activity2.aveStepsIn5Mins <- transform(activity2.aveStepsIn5Mins,day=factor(day))
xyplot(aveSteps~interval|day,data=activity2.aveStepsIn5Mins,layout=c(1,2),type="l")
